A performance assessment of evolutionary algorithms in volunteer computing environments

### 2016-10-28 EvoPar2017/paper.tex
Lo siento, borré la historia...

\documentclass[runningheads,a4paper]{llncs}

@@

\graphicspath{{../img/}}
\DeclareGraphicsExtensions{.pdf}

\begin{document}
%\SweaveOpts{concordance=TRUE}

<<setup, cache=FALSE,echo=FALSE>>=
library("ggplot2")
experiment.data <- data.frame(Experiment=character(),
                              milliseconds=character(),                           
                              IPs=character(), 
                              actualIPs=character(),
                              PUTs=character(),
                              actualPUTs=character(),
                              PUTratio = character(),
                              PUTsIP =character())

these.experiments <- c("nooverlap-1","nooverlap-newgraph-1", "nooverlap-newgraph-2","nooverlap-newgraph-reboot","nooverlap-newgraph-reboot-cachecrash")

experiment.aggregates <- data.frame(Experiment=character(),
                                    milliseconds=character(),
                                    IPs=character(),
                                    actualIPs = character(),
                                    PUTs = character(),
                                    actualPUTs = character(),
                                    count = character(),
                                    totalIPs = character(),
                                    PUTsIP = character())

experiment.aggregates.filtered = experiment.aggregates

ips.data <- data.frame(Experiment=character(),                      
                       PUTs=character(),
                       reboots=character(),
                       idu=character(),
                       idx=character())

ips.aggregates <- data.frame(Experiment=character(),
                             PUTs = character(),
                             reboots = character(),
                             avgPUTs = character(),
                             avgreboots = character(),
                             totalIPs = character())

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-time-cache-2016-03-cache=32-",i,".csv"))

    this.ip.data <- read.csv(paste0("../data/2016-PPSN/ips-reboots-cache=32-",i,".csv"))
    this.len <- length(this.ip.data$PUTs)
    seq <- 1:this.len
    ips.data <- rbind(ips.data,
                      data.frame(Experiment=rep(i,length(this.ip.data$PUTs)),
                                 idu=seq,
                                 idx=seq/this.len,
                                 PUTs=as.integer(this.ip.data$PUTs),
                                 reboots=as.integer(this.ip.data$reboots))
                       )

    ips.aggregates <- rbind( ips.aggregates,
                            data.frame(Experiment=i,
                                       PUTs = median(this.ip.data$PUTs),
                                       reboots = median(this.ip.data$reboots),
                                       avgPUTs = mean(this.ip.data$PUTs),
                                       avgreboots = mean(this.ip.data$reboots),
                                       totalIPs =this.len )
                            )

    experiment.aggregates <- rbind( experiment.aggregates,
                                   data.frame( Experiment=i,                   
                                              milliseconds=median(as.integer(this.data$milliseconds)),
                                              IPs=median(as.integer(this.data$IPs)),
                                              actualIPs=median(as.integer(this.data$actualIPs)),
                                              PUTs=median(as.integer(this.data$PUTs)),
                                              actualPUTs=median(as.integer(this.data$actualPUTs)),
                                              PUTratio=median(as.integer(this.data$actualPUTs)/as.integer(this.data$PUTs)),
                                              count= length(this.data$IPs),
                                              totalIPs=this.len,
                                              PUTsIP=median(as.integer(this.data$PUTs)/as.integer(this.data$IPs)))
                                   )

    experiment.data <- rbind( experiment.data,
                             data.frame( Experiment=rep(i, length(this.data$IPs)),                   
                                        milliseconds=as.integer(this.data$milliseconds),
                                        IPs=as.integer(this.data$IPs),
                                        actualIPs=as.integer(this.data$actualIPs),
                                        PUTs=as.integer(this.data$PUTs),
                                        actualPUTs=as.integer(this.data$actualPUTs),
                                        PUTsIP=as.integer(this.data$PUTs)/as.integer(this.data$IPs)))

    this.data <- this.data[this.data$actualPUTs>=16,]
    experiment.aggregates.filtered <- rbind( experiment.aggregates.filtered,
                                            data.frame( Experiment=i,                   
                                                       milliseconds=median(as.integer(this.data$milliseconds)),
                                                       IPs=median(as.integer(this.data$IPs)),
                                                       actualIPs=median(as.integer(this.data$actualIPs)),
                                                       PUTs=median(as.integer(this.data$PUTs)),
                                                       actualPUTs=median(as.integer(this.data$actualPUTs)),
                                                       count= length(this.data$IPs),
                                                       PUTsIP=median(as.integer(this.data$PUTs)/as.integer(this.data$IPs))
                                                       )
                                            )

}

experiment.data$newgraph <- grepl("newgraph",experiment.data$Experiment)
experiment.data$nooverlap <- grepl("nooverlap",experiment.data$Experiment)
experiment.data$reboot <- grepl("reboot",experiment.data$Experiment)
experiment.data$cachecrash <- grepl("cache",experiment.data$Experiment)

time.data <- data.frame(Experiment=character(),
                        minute=as.Date(character()),
                        IPs=character())

these.experiments <- c("nooverlap-0","nooverlap-newgraph","nooverlap-newgraph-reboot","nooverlap-newgraph-reboot-cachecrash")
ip.correlations <- data.frame(Experiment=character(),
                              correlation=character())

for ( i in these.experiments ) {
    this.data <- read.csv(paste0("../data/2016-PPSN/ips-per-minute-cache=32-",i,".csv"))
    this.data.plus1 <- this.data[2:length(this.data$IPs),]
    ip.correlations <- rbind(ip.correlations, 
                             data.frame(Experiment=i,
                                        correlation = cor(this.data[c(1:length(this.data$IPs)-1),]$IPs
                                                         ,this.data.plus1$IPs)))
    time.data <- rbind(time.data,
                       data.frame(Experiment=rep(i,length(this.data$IPs)),
                                  minute=strptime(this.data$time,"%Y-%m-%d %H:%M"),
                                  IPs=as.integer(this.data$IPs))
                       )
}

@

@@

%
%
\begin{figure}[htbp]
\centering
<<zipf, cache=FALSE,echo=FALSE,fig.height=3>>=
ggplot(ips.data,aes(x=idx,y=PUTs,group=Experiment,color=Experiment))+geom_point()+scale_y_log10()+ scale_colour_discrete(labels=c('base','graph1','graph2','reboot','cachereboot'))+scale_x_log10()
@ %def graph for IPs and puts
%
\caption{Log-log plot of ranked and normalized number of contributions (PUTs) per IP.\label{fig:zipf}}
\end{figure}
%
Every run had slightly different conditions, although in some cases it
was just a server reboot and a new round of announcements. Each run
batch included at least 30 completions, that is, evolution until the
solution was found. The number of runs was controlled by polling an
URL that indicated the number of runs made in the present batch so
far. Every volunteer contributed a certain number of individuals
(represented by the PUT HTTP request) to the server. The ranked number
of contributions per unique IP is shown in Figure \ref{fig:zipf} in a
log-log scale. Besides following the usual Zipf's law found in our
previous work and thus having a very similar appearance for all 5 sets, it
is interesting to see how some sets have a number of contributions per
IP that are slightly superior to the rest, specially so in {\tt
  graph2}. The last two sets, {\tt reboot} and {\tt cachereboot}, also
show a regime in the middle of the graph that shows that some users
are contributing more than in other similar sets. In general, these
differences in behavior are due more to the specific users that show
up in these experiments than to general laws, but it should also be
noted that those behaviors can be encouraged by design.

@@

\begin{table}[htbp]
  \caption{Minute-wise correlation for number of participating volunteers. \label{tab:correlation}}
\begin{center}
<<correlations, cache=FALSE,echo=FALSE>>=
ip.correlations$Experiment <- c("base","graph1","reboot","cachereboot")
kable(ip.correlations)
@ %def correlations
\end{center}
\end{table}
%
We can check this impact by looking at the column that refers to
median time in Table \ref{tab:filtered} and its relation to the median
number of PUTs, which reflects the number of evaluations performed by
the clients. The last two rows have a low number of evaluations,
around 650, which is higher than the first two, probably due to the
lower volunteer supply, but better than the middle one; besides, the
amount is remarkably similar. But in the last case, it takes much less
time to find the solution {\em using the same number of
  evaluations}; the same situation applies if we compare {\tt graph1}
to {\tt cachereboot}. All variables are difficult to control in this
environment, but it might be due to the fact that parallelism has
increased, there are more volunteers contributing at the same time. In
fact, as it can be seen in the last column, the median number of
contributions per user is the lowest for {\tt cachereboot}, which so needs less contributions by users to
find the same solution. Besides, the last row shows that {\em all}
users actively contribute to the cache, while in the {\tt reboot}
strategy 30\% of users do not. This might be due to the fact that {\tt
  reboot} only does so when cache size is less than one, indicating
that this strategy is only partly successful in avoiding overlaps.

>>>>

\documentclass[runningheads,a4paper]{llncs}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}

@@

\graphicspath{{../img/}}
\DeclareGraphicsExtensions{.pdf}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

%
%
\begin{figure}[htbp]
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/zipf-1}

\end{knitrout}
%
\caption{Log-log plot of ranked and normalized number of contributions (PUTs) per IP.\label{fig:zipf}}
\end{figure}
%
Every run had slightly different conditions, although in some cases it
was just a server reboot and a new round of announcements. Each run
batch included at least 30 completions, that is, evolution until the
solution was found. The number of runs was controlled by polling an
URL that indicated the number of runs made in the present batch so
far. Every volunteer contributed a certain number of individuals
(represented by the PUT HTTP request) to the server. The ranked number
of contributions per unique IP is shown in Figure \ref{fig:zipf} in a
log-log scale. Besides following the usual Zipf's law found in our
previous work and thus having a very similar appearance for all 5 sets, it
is interesting to see how some sets have a number of contributions per
IP that are slightly superior to the rest, specially so in {\tt
  graph2}. The last two sets, {\tt reboot} and {\tt cachereboot}, also
show a regime in the middle of the graph that shows that some users
are contributing more than in other similar sets. In general, these
differences in behavior are due more to the specific users that show
up in these experiments than to general laws, but it should also be
noted that those behaviors can be encouraged by design.

@@

\begin{table}[htbp]
  \caption{Minute-wise correlation for number of participating volunteers. \label{tab:correlation}}
\begin{center}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\begin{tabular}{l|r}
\hline
Experiment & correlation\\
\hline
base & 0.8408602\\
\hline
graph1 & 0.7346538\\
\hline
reboot & 0.7280738\\
\hline
cachereboot & 0.4657099\\
\hline
\end{tabular}

\end{knitrout}
\end{center}
\end{table}
%
We can check this impact by looking at the column that refers to
median time in Table \ref{tab:filtered} and its relation to the median
number of PUTs, which reflects the number of evaluations performed by
the clients. The last two rows have a low number of evaluations,
around 650, which is higher than the first two, probably due to the
lower volunteer supply, but better than the middle one; besides, the
amount is remarkably similar. But in the last case, it takes much less
time to find the solution {\em using the same number of
  evaluations}; the same situation applies if we compare {\tt graph1}
to {\tt cachereboot}. All variables are difficult to control in this
environment, but it might be due to the fact that parallelism has
increased, there are more volunteers contributing at the same time. In
fact, as it can be seen in the last column, the median number of
contributions per user is the lowest for {\tt cachereboot}, which so needs less contributions by users to
find the same solution. Besides, the last row shows that {\em all}
users actively contribute to the cache, while in the {\tt reboot}
strategy 30\% of users do not. This might be due to the fact that {\tt
  reboot} only does so when cache size is less than one, indicating
that this strategy is only partly successful in avoiding overlaps.
